Grupo Bimbo Inventory Demand \\Data Science Report

### 2024-07-15 src/data-science-project/data_science_project/docs/report/report.tex
Heatmap Correlation
Business Questions

\section{Feature Engineering}
Feature engineering involved creating new variables to capture additional information and improve model performance.
\begin{itemize}
    \item Temporal Features: Lagged variables were created to capture temporal dependencies in sales and demand.
    \item Economic Indicators: The bi-weekly inflation rate and consumer confidence index were added as features to capture the impact of economic conditions on product demand.
    \item Categorical Encoding: Categorical variables were converted to numerical format using one-hot encoding or label encoding.
\end{itemize}

@@

\section{Business Questions}
The study aimed to address several business questions related to inventory management and demand forecasting:
\begin{itemize}
    \item How can accurate demand forecasting improve inventory management?
    \begin{itemize}
        \item By predicting adjusted demand, Grupo Bimbo can optimize stock levels, reduce waste, and improve resource allocation.
    \end{itemize}
    \item What is the impact of economic indicators on product demand?
    \begin{itemize}
        \item The inclusion of bi-weekly inflation and consumer confidence index data provides insights into how economic conditions influence demand, allowing for more informed decision-making.
    \end{itemize}
\end{itemize}

>>>>

\section{Feature Engineering}
Feature engineering involved creating new variables to capture additional information and improve model performance.
\begin{itemize}
    \item Temporal Features: Lagged variables were created to capture temporal dependencies in sales and demand.
    \item Economic Indicators: The bi-weekly inflation rate and consumer confidence index were added as features to capture the impact of economic conditions on product demand.
    \item Categorical Encoding: Categorical variables were converted to numerical format using one-hot encoding or label encoding.

\begin{figure}[H] 
    \begin{center}
    \centering
    \includegraphics[width=0.9\textwidth]{images/output.png}
    \caption{Heatmap correlation of the features}
    \end{center}
\end{figure}

\end{itemize}

@@

\section{Business Questions}
The study aimed to address several business questions related to inventory management and demand forecasting:
\begin{itemize}
    \item What are our best and worst customers?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/quest1.png}
        \caption{Business Question 1}
        \end{center}
    \end{figure}

    \item What is the relationship between sales growth rates (1 and 2) and adjusted demand?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/quest2.png}
        \caption{Business Question 2}
        \end{center}
    \end{figure}

    \item How are our sales going against the returns, and our adjusted demand?

    % \begin{figure}[H] 
    %     \begin{center}
    %     \centering
    %     \includegraphics[width=0.9\textwidth]{images/quest2.png}
    %     \caption{Business Question 3}
    %     \end{center}
    % \end{figure}

    \item What are our most used routes?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/quest4.png}
        \caption{Business Question 3}
        \end{center}
    \end{figure}

\end{itemize}
